Automated Essay Scoring

### 2018-05-10 paper/acl17-latex/paper.tex
Added introduction

The following instructions are directed to authors of papers submitted
to ACL-2017 or accepted for publication in its proceedings. All
authors are required to adhere to these specifications. Authors are
required to provide a Portable Document Format (PDF) version of their
papers. \textbf{The proceedings are designed for printing on A4
paper.}

>>>>

Automated essay scoring refers to the process of grading student essays without human interference. An AES system takes as input an essay written for a given prompt, and then assigns a numeric score to the essay reflecting its quality, based on its  content, grammar, and organization.

Our experiments on the AES systems aims to test the response of models to spelling and grammatical errors. It also tests if the model really considers the flow of ideas and organization of essay. Along with this, we also try to test if model recoginzes deviation from topic. Effect of length of essay is also studied. We finally suggest some ways to improve the performance of model on these metrics.

The rest of this paper is organized as follows. Section 2 gives an overview of related work in the literature. Section 3 describes the  details of our experiments, and present and discuss the results of our experimental evaluation in Section 4. Finally, we suggest some ways to improve the models in Section 5 and conclude the paper in Section 6.
